### 2021-07-11 src/paper/data/synthetic_population.tex
Fix figure references.

% workers
Workers are assigned to a daily meeting work group. The group sizes vary to match the
number of daily repeating work contacts reported by working individuals in
\cite{Mossong2008}. These groups only consist of workers that work in the same county.
For a distribution of the number of daily recurring work contacts see
Figure~\ref{n_contacts_work_daily_recurrent}. To match the number of weekly work groups
we match each worker with up to 14 other workers into pairs to match the number of
reported weekly work contacts shown in Figure~\ref{n_contacts_work_weekly_recurrent}.
Each pair is assigned a weekday on which they always meet in the absence of work
policies. 80\% of these contacts are individuals from the same county.
% work contact priority
In the same way children have an educational priority determining if they are entitled to
emergency care workers are assigned a work contact priority that captures how necessary
their work is and to which degree they can work from home. This means that it's always
the same individuals that continue to have work contacts when work from home mandates of
a certain strictness are in place. We use the reduction in work mobility reported by
\cite{Google2021} as a proxy for the share of individuals that do not have work contacts.

% other recurring contacts
In addition to creating groups for educational facilities and work we also have other
recurring contacts to represent things like groups of friends or sports teams that
practice regularly together. Both daily and weekly groups are created analogously to the
work groups but matching the numbers in Figure~\ref{n_contacts_other_daily_recurrent} and
Figure~\ref{n_contacts_other_weekly_recurrent}. In addition, since leisure contacts are
highly assortative by age all individuals that have a daily leisure contact are matched
with a person not only from the same county but also from the same age group.

>>>>

% workers
Workers are assigned to a daily meeting work group. The group sizes vary to match the
number of daily repeating work contacts reported by working individuals in
\cite{Mossong2008}. These groups only consist of workers that work in the same county.
For a distribution of the number of daily recurring work contacts see
Figure~\ref{fig:n_contacts_work_daily_recurrent}. To match the number of weekly work groups
we match each worker with up to 14 other workers into pairs to match the number of
reported weekly work contacts shown in Figure~\ref{fig:n_contacts_work_weekly_recurrent}.
Each pair is assigned a weekday on which they always meet in the absence of work
policies. 80\% of these contacts are individuals from the same county.
% work contact priority
In the same way children have an educational priority determining if they are entitled to
emergency care workers are assigned a work contact priority that captures how necessary
their work is and to which degree they can work from home. This means that it's always
the same individuals that continue to have work contacts when work from home mandates of
a certain strictness are in place. We use the reduction in work mobility reported by
\cite{Google2021} as a proxy for the share of individuals that do not have work contacts.

% other recurring contacts
In addition to creating groups for educational facilities and work we also have other
recurring contacts to represent things like groups of friends or sports teams that
practice regularly together. Both daily and weekly groups are created analogously to the
work groups but matching the numbers in Figure~\ref{fig:n_contacts_other_daily_recurrent} and
Figure~\ref{fig:n_contacts_other_weekly_recurrent}. In addition, since leisure contacts are
highly assortative by age all individuals that have a daily leisure contact are matched
with a person not only from the same county but also from the same age group.

### 2021-07-11 src/paper/results/rapid_tests_statistics.tex
Fix figure references.

\subsection{Rapid Tests}
\label{subsec:appendix_rapid_tests}

>>>>

\subsection{Rapid Test Statistics}
\label{subsec:results_rapid_test_statistics}

An important feature in our model is that our rapid tests are imperfectly specific and
imperfectly sensitive. Especially when people have not become infectious yet they are
likely to return a false positive result. Here we look at how rapid tests expanded over
time and to what degree they are useful as a screening device despite missing positive
cases and returning false positive results.

We start with the share of the population doing a rapid test, receiving a positive rapid
test and receiving a negative rapid test over time by the channel through which the test
was demanded in Figures~\ref{fig:rapid_test_demand_by_channel,
fig:pos_rapid_tests_by_channel} and \ref{fig:neg_rapid_tests_by_channel} respectively.
Overall, the share of the population getting a rapid test on a given day increases from
2\% in Mid March to over 10\% by May. The work rapid tests are a little ragged because of
public holidays and weekend effects that lead to jumps around Mondays. For education
rapid tests both vacations (first half of April) as well as the opening of schools in May
are very visible in the rapid test demand. Overall, work tests make up the largest
fraction of rapid tests. The image is very similar for the share of positive tests,
except that the overall number of positive tests starts decreasing in May as rapid test
expansion comes to a halt and cases fall, especially the positive share of private rapid
tests falls as less and less individuals seek a rapid test because of a positive test in
their household.
